Zero-shot task adaptation by homoiconic meta-mapping

### 2019-11-11 writing/homoiconic_meta_mapping_appendix.tex
Iclr revision version

\appendix
The supplemental material is organized as follows: In section \ref{app_clarifying_meta_mapping} we clarify some definitional details, and discuss the value of meta-mappings in detail by comparing to other methods of performing a new task. In section 
\ref{app_continual} we describe a continual-learning like perspective based on our approach. In section \ref{app_supp_figures} we provide supplemental figures. In section \ref{app_cards_tsne} we show $t$-sne results for the cards domain. In section \ref{app_lesion_results} we provide some lesion studies. In section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses. In section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper. \par

@@

\subsection{Why meta-map from tasks to tasks?} \label{app_why_meta_mapping}
Why are meta-mappings between tasks useful? To answer this, we consider various ways of adapting to a new task in figure \ref{fig_why_meta_mapping} (based on results from the cards domain, section \ref{sec_cards}). The system could adapt from seeing examples of the new task, but this requires going out and collecting data, which may be expensive and does not allow zero-shot adaptation. Alternatively, the system could perform the new task via a meta-mapping from a prior learned task, where the meta-mapping is either induced from examples of the meta-mapping, or from language. Finally, the system could perform a new task from language alone, if it is trained to map instructions to tasks. \par
To address this latter possibility, we trained a version of the model where we included training the language system to produce embeddings for the basic tasks (while simultaneously training the system on all the other objectives, such as performing the tasks from examples, in order to provide the strongest possible structuring of the system's knowledge for the strongest possible comparison). We compare this model's performance at held-out tasks to that of systems learning from examples of the new task directly, or from meta-mapping, see fig. \ref{fig_why_meta_mapping}. \par 
These results demonstrate the advantage of meta-mapping. While learning from examples is still better given enough data, it requires potentially-expensive data collection and does not allow zero-shot adaptation. Performing the new task from a language description alone uses only the implicit knowledge in the model's weights, and likely because of this it does not generalize well to the difficult held-out tasks. Meta-mapping performs substantially better, while relying only on cached prior knowledge, viz. prior task-embedding(s) and a description of the meta-mapping (either in the form of examples or natural language). That is, meta-mapping has the advantage of requiring no new data collection, like performing from language alone, but results in much better performance by leveraging a richer description of the new task constructed using the system's knowledge of a prior task and the new task's relationship to it.\par 

@@

\includegraphics[width=\textwidth]{figures/why_meta_mapping.png}
\caption{Comparison of a variety of methods for performing one of the 10\% held-out tasks in the more difficult hold-out set in the cards domain. There are a number of ways the system could adapt to a new task: from seeing example of the new task, from hearing the new task described from language alone, or from leveraging its knowledge about prior tasks via meta-mappings (in this case, from the non-losers variations of the same games). The meta-mappings offer a happy medium between the other two alternatives -- they only require cached knowledge of prior tasks, rather than needing to collect experience on the task before a policy can be derived, but they outperform a system that simply tries to construct the task embedding from a description alone. Language alone is not nearly as rich a cue as knowledge of how a new task relates to prior tasks.} 
\label{fig_why_meta_mapping}

@@

To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in fig. \ref{poly_continual_results}. The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp. fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\begin{figure}[H]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
\caption{The polynomials domain, section \ref{sec_poly}.}
\label{supp_poly_integration_results}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
\caption{The cards domain, section \ref{sec_cards}.}
\label{supp_cards_integration_results}
\end{subfigure}%
\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
\label{supp_integration_results}
\end{figure}

\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

@@

\subsection{Shared $Z$ vs. separate task-embedding and data-embedding space} \label{app_lesion_results_shared_z}
Instead of having a shared $Z$ where data and tasks are embedded, why not have a separate embedding space for data, tasks, and so on? There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}. In this section, we further show that training with a separate task encoding space worsens performance, see fig. \ref{supp_lesion_shared_z_fig}. This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see fig. \ref{supp_lesion_shared_z_learn_fig}. (It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input. Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks. We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks. While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par 
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_results_unshared_vs_shared.png}
\caption{Having a separate embedding space for tasks results in worse performance on meta-mappings. (Results are from only 1 run.)}
\label{supp_lesion_shared_z_fig}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves_with_separate.png}
\caption{Having a separate embedding space for tasks results in noisier, slower learning of meta-mappings. (Results are from only 1 run.)}
\label{supp_lesion_shared_z_learn_fig}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks. Results are from only 2 runs.}
\label{supp_lesion_hyper}
\end{figure}

@@

Note that there are three kinds of hold-out in the training of this system, see section \ref{app_clarifying_holdouts}. \par

@@

\subsection{Source repositories}
The full code for the experiments and analyses can be found on github:
\begin{itemize}
\item \url{https://github.com/lampinen/polynomials}
    \begin{itemize}
        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
    \end{itemize}
\item \url{https://github.com/lampinen/meta_cards} 
\end{itemize}
\section{Numerical results} \label{app_numerical_results}
In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures. Tables were generated with stargazer \citep{Hlavac2018}. \par

\subsection{Polynomials}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
HoMM & Trained & 0.015 & 0.012 & 0.018 \\
HoMM & Held out & 0.246 & 0.188 & 0.308 \\
Untrained HoMM network & Trained & 5.735 & 4.823 & 6.74 \\
Untrained HoMM network & Held out & 5.968 & 4.984 & 6.991 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, figure \ref{poly_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
HoMM & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
HoMM & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
HoMM & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
HoMM & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
Untrained HoMM network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
Untrained HoMM network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
Untrained HoMM network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
Untrained HoMM network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for meta-mapping results from examples, figure \ref{poly_meta_map_results_examples}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
\hline \\[-1.8ex] 
Language & Trained mapping, on trained task & 0.515 & 0.483 & 0.552 \\ 
Language & Trained mapping, on held-out task & 2.244 & 1.921 & 2.623 \\ 
Language & Held-out mapping, on trained task & 2.072 & 1.958 & 2.19 \\ 
Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
Untrained HoMM network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
Untrained HoMM network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
Untrained HoMM network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
Untrained HoMM network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
\hline \\[-1.8ex] 
\end{tabular}
\caption{Table for meta-mapping results from language, figure \ref{poly_meta_map_results_language}}
\end{table}

\subsection{Cards}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & named\_game\_type & is\_new\_game & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
\hline \\[-1.8ex]
Random 50\% holdout & High card & Trained & 0.53 & 0.521 & 0.541 \\
Random 50\% holdout & High card & Held out & 0.441 & 0.42 & 0.462 \\
Random 50\% holdout & Match & Trained & 0.537 & 0.524 & 0.55 \\
Random 50\% holdout & Match & Held out & 0.539 & 0.523 & 0.556 \\
Random 50\% holdout & Pairs & Trained & 0.521 & 0.504 & 0.536 \\
Random 50\% holdout & Pairs & Held out & 0.453 & 0.434 & 0.47 \\
Random 50\% holdout & Straight flush & Trained & 0.525 & 0.508 & 0.54 \\
Random 50\% holdout & Straight flush & Held out & 0.484 & 0.466 & 0.502 \\
Random 50\% holdout & Blackjack & Trained & 0.582 & 0.557 & 0.603 \\
Random 50\% holdout & Blackjack & Held out & 0.492 & 0.468 & 0.513 \\
Targeted 10\% holdout & High card & Trained & 0.527 & 0.518 & 0.536 \\
Targeted 10\% holdout & Match & Trained & 0.536 & 0.526 & 0.546 \\
Targeted 10\% holdout & Pairs & Trained & 0.522 & 0.512 & 0.531 \\
Targeted 10\% holdout & Straight flush & Trained & 0.524 & 0.509 & 0.538 \\
Targeted 10\% holdout & Straight flush & Held out & 0.361 & 0.332 & 0.39 \\
Targeted 10\% holdout & Blackjack & Trained & 0.586 & 0.575 & 0.598 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Trained & Targeted 10\% holdout & High card & 0.531 \\
Trained & Targeted 10\% holdout & Match & 0.541 \\
Trained & Targeted 10\% holdout & Pairs & 0.532 \\
Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
Trained & Random 50\% holdout & High card & 0.531 \\
Held out & Random 50\% holdout & High card & 0.396 \\
Trained & Random 50\% holdout & Match & 0.541 \\
Held out & Random 50\% holdout & Match & 0.541 \\
Trained & Random 50\% holdout & Pairs & 0.532 \\
Held out & Random 50\% holdout & Pairs & 0.37 \\
Trained & Random 50\% holdout & Straight flush & 0.536 \\
Held out & Random 50\% holdout & Straight flush & 0.452 \\
Trained & Random 50\% holdout & Blackjack & 0.595 \\
Held out & Random 50\% holdout & Blackjack & 0.456 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Blackjack & 0.592 \\
High card & 0.531 \\
Match & 0.541 \\
Pairs & 0.532 \\
Straight flush & 0.536 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for playing optimal rewards for basic meta-learning, solid lines in figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Trained & Targeted 10\% holdout & High card & 0.531 \\
Trained & Targeted 10\% holdout & Match & 0.541 \\
Trained & Targeted 10\% holdout & Pairs & 0.532 \\
Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
Trained & Random 50\% holdout & High card & 0.531 \\
Held out & Random 50\% holdout & High card & 0.396 \\
Trained & Random 50\% holdout & Match & 0.541 \\
Held out & Random 50\% holdout & Match & 0.541 \\
Trained & Random 50\% holdout & Pairs & 0.532 \\
Held out & Random 50\% holdout & Pairs & 0.37 \\
Trained & Random 50\% holdout & Straight flush & 0.536 \\
Held out & Random 50\% holdout & Straight flush & 0.452 \\
Trained & Random 50\% holdout & Blackjack & 0.595 \\
Held out & Random 50\% holdout & Blackjack & 0.456 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
\hline \\[-1.8ex]
Targeted 10\% holdout & Switch suits & Trained & 0.523 & 0.512 & 0.534 \\
Targeted 10\% holdout & Switch suits & Held out & 0.234 & 0.196 & 0.273 \\
Targeted 10\% holdout & Losers & Trained & 0.532 & 0.511 & 0.546 \\
Targeted 10\% holdout & Losers & Held out & 0.289 & 0.241 & 0.322 \\
Random 50\% holdout & Switch suits & Trained & 0.528 & 0.521 & 0.533 \\
Random 50\% holdout & Switch suits & Held out & 0.375 & 0.368 & 0.382 \\
Random 50\% holdout & Losers & Trained & 0.531 & 0.523 & 0.538 \\
Random 50\% holdout & Losers & Held out & 0.427 & 0.417 & 0.436 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for meta-mapping from examples, figure \ref{cards_meta_map_results_examples}}
\end{table}

>>>>

\appendix
The supplemental material is organized as follows: In Section \ref{app_clarifying_meta_mapping} we clarify some definitional details. In Section 
\ref{app_continual} we describe a continual-learning like perspective based on our approach. In Section \ref{app_supp_figures} we provide supplemental figures. In Section \ref{app_cards_tsne} we show $t$-sne results for the cards domain. In Section \ref{app_lesion_results} we provide some lesion studies. In Section \ref{app_detailed_methods} we list details fo the datasets and architectures we used, as well as providing links to the source code for all models, experiments, and analyses. In Section \ref{app_numerical_results} we provide means and bootstrap CIs corresponding to the major figures in the paper. \par

@@

@@

@@

To test this idea, we pre-trained the system on 100 polynomial tasks, and then introduced 100 new tasks. We trained on these new tasks by starting from the meta-network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. The results are shown in Fig. \ref{poly_continual_results}. The meta-network embeddings offer good immediate performance, and substantially accelerate the optimization process, compared to a randomly-initialized embedding (see supp. Fig. \ref{supp_poly_continual_results} for a more direct comparison). Furthermore, this ability to learn is due to training, not simply the expressiveness of the architecture, as is shown by attempting the same with an untrained network. \par

@@

\begin{figure}[H]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/basic_results_over_time.png}
\caption{The polynomials domain, Section \ref{sec_poly}.}
\label{supp_poly_integration_results}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/basic_meta_learning_integrating_over_time.png}
\caption{The cards domain, Section \ref{sec_cards}.}
\label{supp_cards_integration_results}
\end{subfigure}%
\caption{Integrating new tasks into the system by training all parameters results in some initial interference with prior tasks (even with replay), suggesting that an approach like the continual learning-approach may be useful.}
\label{supp_integration_results}
\end{figure}

\section{Card game $t$-SNE} \label{app_cards_tsne}
We performed $t$-SNE \citep{LaurensvanderMaaten2008} on the task embeddings of the system at the end of learning the card game tasks, to evaluate the organization of knowledge in the network. In Fig. \ref{fig_cards_tsne_basic} we show these embeddings for just the basic tasks. The embeddings show systematic grouping by game attributes. In Fig. \ref{fig_cards_tsne_full} we show the embeddings of the meta and basic tasks, showing the organization of the meta-tasks by type. \par 
\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{figures/basic_tsne_basic_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the basic card game tasks. (Note that the pairs of nearby embeddings differ in the ``suits rule`` attribute, discussed in Appendix \ref{meth_data_cards}.)} 
\label{fig_cards_tsne_basic}
\end{figure}%
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{figures/basic_tsne_full_final.png}
\caption{$t$-SNE embedding of the function embeddings the system learned for the meta tasks (basic tasks are included in the background).} 
\label{fig_cards_tsne_full}
\end{figure}

@@

\subsection{Shared $Z$ vs. separate task-embedding and data-embedding space} \label{app_lesion_results_shared_z}
Instead of having a shared $Z$ where data and tasks are embedded, why not have a separate embedding space for data, tasks, and so on? There are a few conceptual reason why we chose to have a shared $Z$, including its greater parameter efficiency, the fact that humans seem to represent our conscious knowledge of different kinds in a shared space \citep[][]{Baars2005}, and the fact that this representation could allow for zero-shot adaptation to new computational pathways through the latent space, analogously to the zero-shot language translation results reported by Johnson and colleagues \citep{Johnson2016a}. In this section, we further show that training with a separate task encoding space worsens performance, see Fig. \ref{supp_lesion_shared_z_fig}. This seems to primarily be due to the fact that learning in the shared $Z$ accelerates and de-noises the learning process, see Fig. \ref{supp_lesion_shared_z_learn_fig}. (It's therefore worth noting that running this model for longer could result in convergence to the same asymptotic generalization performance.) \par
\subsection{Hyper network vs. conditioned task network} \label{app_lesion_results_hyper}
Instead of having the task network $F$ parameterized by the hyper network $\mathcal{H}$, we could simply have a task network with learned weights which takes a task embedding as another input. Here, we show that this architecture fails to learn the meta-mapping tasks, although it can successfully perform the basic tasks. We suggest that this is because it is harder for this architecture to prevent interference between the comparatively larger number of basic tasks and the smaller number of meta-tasks. While it might be possible to succeed with this architecture, it was more difficult in the hyper-parameter space we searched.\par 
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_results_unshared_vs_shared.png}
\caption{Having a separate embedding space for tasks results in worse performance on meta-mappings. (Results are from only 1 run.)}
\label{supp_lesion_shared_z_fig}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_learning_curves_with_separate.png}
\caption{Having a separate embedding space for tasks results in noisier, slower learning of meta-mappings. (Results are from only 1 run.)}
\label{supp_lesion_shared_z_learn_fig}
\end{figure}
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{figures/poly/meta_results_conditioned_vs_hyper.png}
\caption{Conditioning the task network on the task embedding, rather than parameterizing it via a hyper network causes it to fail at the meta-mapping tasks. Results are from only 2 runs.}
\label{supp_lesion_hyper}
\end{figure}

@@

Note that there are three kinds of hold-out in the training of this system, see Section \ref{app_clarifying_holdouts}. \par

@@

\subsection{Source repositories}
(Will be included in de-anonymized version.)
%The full code for the experiments and analyses can be found on github:
%\begin{itemize}
%\item \url{https://github.com/lampinen/polynomials}
%    \begin{itemize}
%        \item See the \verb|continual_learning| and \verb|language_meta_only| branches for the continual learning and language results, respectively. 
%    \end{itemize}
%\item \url{https://github.com/lampinen/meta_cards} 
%\end{itemize}
\section{Numerical results} \label{app_numerical_results}
In this section we provide the mean values and bootstrap confidence intervals corresponding to the major figures in the paper, as well as the baseline results in those figures. Tables were generated with stargazer \citep{Hlavac2018}. \par

\subsection{Polynomials}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & is\_new & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
HoMM & Trained & 0.015 & 0.012 & 0.018 \\
HoMM & Held out & 0.246 & 0.188 & 0.308 \\
Untrained HoMM network & Trained & 5.735 & 4.823 & 6.74 \\
Untrained HoMM network & Held out & 5.968 & 4.984 & 6.991 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, Figure \ref{poly_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\
\hline \\[-1.8ex]
HoMM & Trained mapping, on trained task & 0.094 & 0.091 & 0.098 \\
HoMM & Trained mapping, on held-out task & 1.721 & 1.419 & 2.115 \\
HoMM & Held-out mapping, on trained task & 1.28 & 1.213 & 1.35 \\
HoMM & Held-out mapping, on held-out task & 1.775 & 1.706 & 1.846 \\
Untrained HoMM network & Trained mapping, on trained task & 12.998 & 11.689 & 14.381 \\
Untrained HoMM network & Trained mapping, on held-out task & 15.002 & 13.39 & 16.83 \\
Untrained HoMM network & Held-out mapping, on trained task & 8.36 & 7.898 & 8.833 \\
Untrained HoMM network & Held-out mapping, on held-out task & 8.786 & 8.317 & 9.27 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for meta-mapping results from examples, Figure \ref{poly_meta_map_results_examples}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
named\_run\_type & result\_type & mean\_loss & boot\_CI\_low & boot\_CI\_high \\ 
\hline \\[-1.8ex] 
Language & Trained mapping, on trained task & 0.515 & 0.483 & 0.552 \\ 
Language & Trained mapping, on held-out task & 2.244 & 1.921 & 2.623 \\ 
Language & Held-out mapping, on trained task & 2.072 & 1.958 & 2.19 \\ 
Language & Held-out mapping, on held-out task & 2.35 & 2.254 & 2.447 \\ 
Untrained HoMM network & Trained mapping, on trained task & 13.328 & 11.977 & 14.823 \\ 
Untrained HoMM network & Trained mapping, on held-out task & 15.313 & 13.602 & 17.354 \\ 
Untrained HoMM network & Held-out mapping, on trained task & 8.205 & 7.795 & 8.662 \\ 
Untrained HoMM network & Held-out mapping, on held-out task & 8.625 & 8.131 & 9.104 \\ 
\hline \\[-1.8ex] 
\end{tabular}
\caption{Table for meta-mapping results from language, Figure \ref{poly_meta_map_results_language}}
\end{table}

\subsection{Cards}
\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & named\_game\_type & is\_new\_game & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
\hline \\[-1.8ex]
Random 50\% holdout & High card & Trained & 0.53 & 0.521 & 0.541 \\
Random 50\% holdout & High card & Held out & 0.441 & 0.42 & 0.462 \\
Random 50\% holdout & Match & Trained & 0.537 & 0.524 & 0.55 \\
Random 50\% holdout & Match & Held out & 0.539 & 0.523 & 0.556 \\
Random 50\% holdout & Pairs & Trained & 0.521 & 0.504 & 0.536 \\
Random 50\% holdout & Pairs & Held out & 0.453 & 0.434 & 0.47 \\
Random 50\% holdout & Straight flush & Trained & 0.525 & 0.508 & 0.54 \\
Random 50\% holdout & Straight flush & Held out & 0.484 & 0.466 & 0.502 \\
Random 50\% holdout & Blackjack & Trained & 0.582 & 0.557 & 0.603 \\
Random 50\% holdout & Blackjack & Held out & 0.492 & 0.468 & 0.513 \\
Targeted 10\% holdout & High card & Trained & 0.527 & 0.518 & 0.536 \\
Targeted 10\% holdout & Match & Trained & 0.536 & 0.526 & 0.546 \\
Targeted 10\% holdout & Pairs & Trained & 0.522 & 0.512 & 0.531 \\
Targeted 10\% holdout & Straight flush & Trained & 0.524 & 0.509 & 0.538 \\
Targeted 10\% holdout & Straight flush & Held out & 0.361 & 0.332 & 0.39 \\
Targeted 10\% holdout & Blackjack & Trained & 0.586 & 0.575 & 0.598 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for basic meta-learning, Figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Trained & Targeted 10\% holdout & High card & 0.531 \\
Trained & Targeted 10\% holdout & Match & 0.541 \\
Trained & Targeted 10\% holdout & Pairs & 0.532 \\
Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
Trained & Random 50\% holdout & High card & 0.531 \\
Held out & Random 50\% holdout & High card & 0.396 \\
Trained & Random 50\% holdout & Match & 0.541 \\
Held out & Random 50\% holdout & Match & 0.541 \\
Trained & Random 50\% holdout & Pairs & 0.532 \\
Held out & Random 50\% holdout & Pairs & 0.37 \\
Trained & Random 50\% holdout & Straight flush & 0.536 \\
Held out & Random 50\% holdout & Straight flush & 0.452 \\
Trained & Random 50\% holdout & Blackjack & 0.595 \\
Held out & Random 50\% holdout & Blackjack & 0.456 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for playing most correlated learned strategy for basic meta-learning, dashed colored lines in Figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Blackjack & 0.592 \\
High card & 0.531 \\
Match & 0.541 \\
Pairs & 0.532 \\
Straight flush & 0.536 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for playing optimal rewards for basic meta-learning, solid lines in Figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
is\_new\_game & named\_run\_type & named\_game\_type & expected\_reward \\
\hline \\[-1.8ex]
Trained & Targeted 10\% holdout & High card & 0.531 \\
Trained & Targeted 10\% holdout & Match & 0.541 \\
Trained & Targeted 10\% holdout & Pairs & 0.532 \\
Trained & Targeted 10\% holdout & Straight flush & 0.537 \\
Held out & Targeted 10\% holdout & Straight flush & 0.274 \\
Trained & Targeted 10\% holdout & Blackjack & 0.592 \\
Trained & Random 50\% holdout & High card & 0.531 \\
Held out & Random 50\% holdout & High card & 0.396 \\
Trained & Random 50\% holdout & Match & 0.541 \\
Held out & Random 50\% holdout & Match & 0.541 \\
Trained & Random 50\% holdout & Pairs & 0.532 \\
Held out & Random 50\% holdout & Pairs & 0.37 \\
Trained & Random 50\% holdout & Straight flush & 0.536 \\
Held out & Random 50\% holdout & Straight flush & 0.452 \\
Trained & Random 50\% holdout & Blackjack & 0.595 \\
Held out & Random 50\% holdout & Blackjack & 0.456 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for most correlated baselines for basic meta-learning, dashed colored lines in Figure \ref{cards_basic_results}}
\end{table}

\begin{table}[H]
\scriptsize
\centering
\begin{tabular}{@{\extracolsep{5pt}} cccccc}
\\[-1.8ex]\hline
\hline \\[-1.8ex]
named\_run\_type & named\_meta\_task & is\_new & average\_reward & avg\_rwd\_CI\_low & avg\_rwd\_CI\_high \\
\hline \\[-1.8ex]
Targeted 10\% holdout & Switch suits & Trained & 0.523 & 0.512 & 0.534 \\
Targeted 10\% holdout & Switch suits & Held out & 0.234 & 0.196 & 0.273 \\
Targeted 10\% holdout & Losers & Trained & 0.532 & 0.511 & 0.546 \\
Targeted 10\% holdout & Losers & Held out & 0.289 & 0.241 & 0.322 \\
Random 50\% holdout & Switch suits & Trained & 0.528 & 0.521 & 0.533 \\
Random 50\% holdout & Switch suits & Held out & 0.375 & 0.368 & 0.382 \\
Random 50\% holdout & Losers & Trained & 0.531 & 0.523 & 0.538 \\
Random 50\% holdout & Losers & Held out & 0.427 & 0.417 & 0.436 \\
\hline \\[-1.8ex]
\end{tabular}
\caption{Table for meta-mapping from examples, Figure \ref{cards_meta_map_results_examples}}
\end{table}
